The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2016-04-15 Dissertate-Harvard-LaTeX/chapters/chapter1.tex
upd
update

\noindent The contents of this chapter are published in \textit{Piso, A.-M. A \& Youdin, A. N. Y}

@@

This paper is organized as follows. Section \S\ref{sec:model} describes our model of atmospheric growth.  In Section \S\ref{sec:coolingan}, we develop a simplified analytic version of our atmospheric model.  We describe the structure and evolution of our atmosphere solutions in Section \S\ref{sec:KH}.   Section \S\ref{sec:critical} gives our final results for growth timescales and critical core masses.  We discuss some neglected effects in Section \S\ref{sec:neglected1} and summarize our findings in Section \S\ref{sec:conclusions}.  Some detailed derivations are presented in the appendices.

\section{Atmospheric Accretion Model} \label{sec:model}

@@

We examine the structure and evolution of our model atmospheres, calculated as described in \S\ref{sec:model}.  For comparison, we also show results of the non-self-gravitating analytic model of \S\ref{sec:coolingan}.  Radial structure is presented in \S\ref{sec:profiles}, time evolution is described in \S\ref{sec:timeev}, and the validity of our two-layer cooling model is examined in \S\ref{sec:endoftime}.

>>>>

\noindent The contents of this chapter are published in \textit{Piso, A.-M. A \& Youdin, A. N. 2014, ApJ, 786, 21}

@@

This paper is organized as follows. Section \S\ref{sec:model1} describes our model of atmospheric growth.  In Section \S\ref{sec:coolingan}, we develop a simplified analytic version of our atmospheric model.  We describe the structure and evolution of our atmosphere solutions in Section \S\ref{sec:KH}.   Section \S\ref{sec:critical} gives our final results for growth timescales and critical core masses.  We discuss some neglected effects in Section \S\ref{sec:neglected1} and summarize our findings in Section \S\ref{sec:conclusions}.  Some detailed derivations are presented in the appendices.

\section{Atmospheric Accretion Model} \label{sec:model1}

@@

We examine the structure and evolution of our model atmospheres, calculated as described in \S\ref{sec:model1}.  For comparison, we also show results of the non-self-gravitating analytic model of \S\ref{sec:coolingan}.  Radial structure is presented in \S\ref{sec:profiles}, time evolution is described in \S\ref{sec:timeev}, and the validity of our two-layer cooling model is examined in \S\ref{sec:endoftime}.
